---
title: "Exploratory: Correlation Between Facebook Social Conectedness Index and UN's Migrant Stock"
output:
  html_document:
    css: style.css
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

dir_proj = file.path(dirname(getwd()))
dir_R = file.path(dirname(getwd()), "R")

source(file.path(dir_proj,"set_up.R"))

dir_data = file.path(dir_proj, "1.Data")
dir_raw = file.path(dir_data, "raw_data")
dir_clean = file.path(dir_data, "clean_data")

extrafont::loadfonts(device = "win")

#read data
joint_data = import(file.path(dir_clean, "joint_un_sci_pop_codelist.rds"))

```


<style>
@import url('https://fonts.googleapis.com/css2?family=Roboto&display=swap');
</style>


<style>
@import url('https://fonts.googleapis.com/css2?family=Roboto:wght@100&display=swap');
</style>

<hr>

# Data sources

 
 * **Iso codes, region, and income level:**  `r emo::ji("package")` {wbstats} and `r emo::ji("package")`{countrycodes} R packages. This analysis excludes observations that are not present in the World Bank's list of countries.
 
  
 *  [Facebook's Social Connectedness Index](https://dataforgood.fb.com/docs/social-connectedness-index-methodology/) : It measures the relative probability of a Facebook friendship link between a given Facebook user in location *i* and a user in location *j.* Put differently, if this measure is twice as large, a Facebook user in *i* is about twice as likely to be connected with a given Facebook user in *j*. SCI excludes the following areas: Afghanistan, Western Sahara, China, Cuba, Iraq, Israel, Iran, North Korea, Russia, Syria, Somalia, South Sudan, Sudan, Venezuela, Yemen, Crimea, Jammu and Kashmir, Donetsk, Luhansk, Sevastopol, West Bank, and Gaza.
 
 * [UN Migrant Stock By Origin And Destination](https://www.un.org/en/development/desa/population/migration/data/estimates2/estimates19.asp) : The total migrant stock at mid-year by origin and country of destination
 
 * **World Bank's Total Population** : Total population by country, accessed via `r emo::ji("package")` {wbstats} in R.
 

# Clean data

Because the SCI data contains only information for 2019, the clean version of the "joint/merged" dataset only includes data for this year and for countries that are included in all the data sources (UN Stocks, Facebook SCI, World Bank's Total Population). The _iso codes_ were used to define **A unique bilateral identifier** for each combination of countries. A second identifier was created to identify the direction of the relationship between countries. 

The variables _stocks_bilateral_,  _flow_origin_ and _flow_destination_ were calculated using UN's Migration Stock.

The table below shows 10 rows of the clean data:



```{R, echo= F}



 table = DT::datatable(joint_data %>%
                         filter(stocks_destination >0) %>%
                         filter(row_number() <= 10
                               ) %>%
                         select(-seq, - Code_destination, -Code_origin),
                       rownames = F,
                       options = list(scrollX = TRUE,
                                      dom = 't'
                                      )
                       )
 
 
 table

```
 





# Correlation between SCI and UN bilateral stocks

```{r plot, echo=FALSE, warning=FALSE, out.width = '100%', message=FALSE}

data_un_sci = joint_data %>%
  filter(stocks_bilateral >0)
  
 


ggplot(data = data_un_sci,
       aes(x = log(stocks_bilateral),
           y = log(scaled_sci))
)+
  geom_point(fill = "#8F1838",
             show.legend = F,
             size = 1,
             color = "white",
             shape = 21) +
  geom_smooth(method = "lm",
              color = "#0033A1") +
  
  labs(x = "UN's Bilateral Stock of Migrants (log)",
       y = "Facebook SCI (log)",
       title= "") +
  theme(
    strip.background = element_blank(),
    axis.title = element_markdown(family="Open Sans Light", size = 16),
    panel.background = element_blank(),
    panel.grid.major = element_line(color = "#E3E3E3"),
   
  )


```

<hr>
## By country's income level

```{r plot_income, echo=FALSE, warning=FALSE, out.width = '100%', message=FALSE}

data_un_sci = import(file.path(dir_clean, "joint_un_sci_pop_codelist.rds")) %>%
  filter(stocks_bilateral >100,
         seq == 1) %>%
  mutate(flow_income = str_replace_all(flow_income, "income", ""))
 


ggplot(data = data_un_sci,
       aes(x = log(stocks_bilateral),
           y = log(scaled_sci))
)+
  geom_point(aes(fill = flow_income),
             show.legend = F,
             size = 1,
             color = "white",
             shape = 21) +
  geom_smooth(method = "lm",
              color = "#0033A1") +
  facet_wrap(
    ~flow_income, scales = c("free_y")
  ) +
  labs(x = "UN's Bilateral Stock of Migrants (log)",
       y = "Facebook SCI (log)",
       title= "") +
  theme(
    strip.background = element_blank(),
    strip.text = element_text(hjust = 0, size = 8, family = "Open Sans"),
    axis.title = element_markdown(family="Open Sans Light", size = 16),
    panel.background = element_blank(),
    panel.grid.major = element_line(color = "#E3E3E3"),
    plot.title = element_markdown(family = "Roboto", hjust = .5, size = 20)
  )



```

<hr>
## By country's region

```{r plot_region, echo=FALSE, warning=FALSE, out.width = '100%', message=FALSE}

data_un_sci = import(file.path(dir_clean, "joint_un_sci_pop_codelist.rds")) %>%
  filter(stocks_bilateral >100,
         seq == 1) %>%
  mutate(flow_income = str_replace_all(flow_income, "income", ""))
 


ggplot(data = data_un_sci,
       aes(x = log(stocks_bilateral),
           y = log(scaled_sci))
)+
  geom_point(aes(fill = flow_region),
             show.legend = F,
             size = 1,
             color = "white",
             shape = 21) +
  geom_smooth(method = "lm",
              color = "#0033A1") +
  facet_wrap(
    ~flow_region, scales = c("free_y")
  ) +
  labs(x = "UN's Bilateral Stock of Migrants (log)",
       y = "Facebook SCI (log)",
       title= "") +
  theme(
    strip.background = element_blank(),
    strip.text = element_text(hjust = 0, size = 7.5, family = "Open Sans"),
    axis.title = element_markdown(family="Open Sans Light", size = 16),
    panel.background = element_blank(),
    panel.grid.major = element_line(color = "#E3E3E3"),
    plot.title = element_markdown(family = "Roboto", hjust = .5, size = 20)
  )



```

